%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{xcolor}
\definecolor{accentblue}{RGB}{0, 102, 204} 


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubheadingDense}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-12pt}
}

\newcommand{\resumeSubheadingMedium}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge Zheng Yu} \\ \vspace{2pt}
    \href{mailto:dataisland@outlook.com}{\underline{dataisland@outlook.com}} 
    $|$  \underline{+1 312-520-5936}
\end{center}


\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheadingDense
        {Northwestern University}{Evanston, IL, USA}
        {Ph.D. in Computer Science (Advisor: Prof. Xinyu Xing)}{Sep 2022 -- March 2026}
    \resumeSubheadingDense
        {Shanghai Jiao Tong University}{Shanghai, China}
        {Bachelor of Science in Computer Science $|$ ACM Honors Program}{Sep 2018 -- Jun 2022}
  \resumeSubHeadingListEnd


\section{Core Competencies}
\resumeSubHeadingListStart
  \resumeSubheadingMedium
    {\textbf{High-Impact Open-Source Leadership}}{}
    {\textcolor{accentblue}{5,000+ Combined GitHub Stars} $|$ Industry \& Government Recognition}
    {}
    \resumeItemListStart
      \resumeItem{\textbf{Project Leadership:} Created \textcolor{accentblue}{GPT-Fuzzer (500+ stars)}, an LLM robustness testing framework integrated into Microsoft Azure's PyRIT security toolkit. Developed \textcolor{accentblue}{PatchAgent (100+ stars)}, an AI-powered automated program repair system that achieved DARPA AIxCC finalist status among 50+ international teams.}
      \resumeItem{\textbf{Core Maintainer Contributions:} Served as core developer for \textcolor{accentblue}{Qiling Framework (5,000+ stars)}, implementing hardware emulation modules. Contributed security patches and performance improvements to critical infrastructure projects including Linux Kernel, PHP interpreter, Assimp, GPAC, and Yasm assembler.}
      \resumeItem{\textbf{Competitive Programming Excellence:} \textcolor{accentblue}{Silver medalist at China National Olympiad in Informatics (NOI 2017)}, ranking top 100 among 10,000+ participants nationwide. Leveraged algorithmic expertise as Teaching Assistant for competitive programming and data structures courses at Shanghai Jiao Tong University.}
      \resumeItem{\textbf{Full-Stack Engineering:} Architected and deployed end-to-end systems across the technology stack. Expert proficiency in front-end technologies (JavaScript, React, CSS), back-end development (C/C++, Python, Java, Go, Rust), and cloud-native infrastructure (Docker, Kubernetes, CI/CD pipelines) for production-grade applications.}
    \resumeItemListEnd
    \resumeSubheadingMedium
    {\textbf{Pioneering Agentic System Design for Security Purpose}}{}
    {\textcolor{accentblue}{IEEE S\&P \& USENIX Security Publications} $|$ DARPA AIxCC Finalist}
    {}
    \resumeItemListStart
      \resumeItem{\textbf{Patch Backporting Agent:} First-authored \textcolor{accentblue}{PortGPT}, an LLM-based agent system for automated backporting with hierarchical workflow design to mitigate hallucination and context limitations. Published at IEEE S\&P 2026 and backported 9 Linux kernel patches from mainline to stable versions, garnering coverage by tech media.}
      \resumeItem{\textbf{Automated Vulnerability Repair:} First-authored \textcolor{accentblue}{PatchAgent} with innovative middleware layer between LLM and execution environment, enabling enhanced tool utilization. Accepted at USENIX Security 2025 and repaired 10 real-world CVEs across open-source projects including Pcapplusplus, libredwg, Assimp, libssh2, and HDF5.}
      \resumeItem{\textbf{End-to-End DARPA AIxCC System:}
      Core team member of 42-b3yond-6ug at DARPA AIxCC, architecting \textcolor{accentblue}{BugBuster}—an LLM-powered system for automated vulnerability discovery and repair. Advanced to finalist position among 50+ international teams.}
    \resumeItemListEnd
    \resumeSubheadingMedium
    {\textbf{Deep Expertise in Low-Level Security \& Systems}}{}
    {\textcolor{accentblue}{50+ CVE Discoveries} $|$ Compiler-Based Defenses $|$ Highly-Cited AI Security Research}
    {}
    \resumeItemListStart
      \resumeItem{\textbf{Compiler \& Kernel Security:} First-authored \textcolor{accentblue}{ShadowBound} and co-authored \textcolor{accentblue}{CAMP} for userspace and kernel hardening, both published at USENIX Security. Implemented custom LLVM optimization passes, showing mastery of compiler and low-level memory management across privilege boundaries.}
      \resumeItem{\textbf{Vulnerability \& Exploit Study:} Discovered \textcolor{accentblue}{50+ CVEs} across userspace applications and the Linux kernel through systematic security analysis. \textcolor{accentblue}{Top 5 finalist at DEFCON CTF Finals (2022-2023)} with team StrawHat, showcasing deep understanding of binary exploitation and defense mechanisms.}
      \resumeItem{\textbf{AI Security Research Impact:} Co-authored \textcolor{accentblue}{GPT-Fuzzer} (published as LLM-Fuzzer at USENIX Security 2024), which has become a foundational work in LLM jailbreak assessment. The framework was integrated into Microsoft Azure's PyRIT security toolkit.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Publications}
\small{\textit{* denotes equal contribution}}
\resumeSubHeadingListStart
\resumeSubItem{
    \textbf{Patch Validation in Automated Vulnerability Repair} \\
    \textit{\textbf{Zheng Yu}, Wenxuan Shi, Xinqian Sun, Zheyun Feng, Meng Xu, Xinyu Xing} \\
    \textit{arXiv 2603.06858} \\
  }
  \resumeSubItem{
    \textbf{pPatch: Automated Vulnerability Unpatching} \\
    \textit{Tianyi Jing, Pengyu Ding, Meng Xu, Yinhao Hu, \textbf{Zheng Yu}, Dongliang Mu} \\
    \textit{ACM International Conference on the Foundations of Software Engineering (FSE) 2026}
  }
  \resumeSubItem{
    \textbf{PortGPT: Towards Automated Backporting Using Large Language Models} \\
    \textit{\textbf{Zheng Yu*}, Zhaoyang Li*, Jingyi Song, Meng Xu, Yuxuan Luo, Dongliang Mu} \\
    \textit{IEEE Symposium on Security and Privacy (S\&P) 2026}
  }
  \resumeSubItem{
    \textbf{PatchAgent: A Practical Program Repair Agent Mimicking Human Expertise} \\
    \textit{\textbf{Zheng Yu}, Ziyi Guo, Yuhang Wu, Jiahao Yu, Meng Xu, Dongliang Mu, Yan Chen, Xinyu Xing} \\
    \textit{USENIX Security Symposium 2025}
  }
  \resumeSubItem{
    \textbf{ShadowBound: Efficient Heap Memory Protection Through Advanced Metadata Management and Customized Compiler Optimization} \\
    \textit{\textbf{Zheng Yu}, Ganxiang Yang, Xinyu Xing} \\
    \textit{USENIX Security Symposium 2024}
  }
  \resumeSubItem{
    \textbf{LLM-Fuzzer: Scaling Assessment of Large Language Model Jailbreaks} \\
    \textit{Jiahao Yu, Xingwei Lin, \textbf{Zheng Yu}, Xinyu Xing} \\
    \textit{USENIX Security Symposium 2024}
  }
  \resumeSubItem{
    \textbf{CAMP: Compiler and Allocator-based Heap Memory Protection} \\
    \textit{Zhenpeng Lin, \textbf{Zheng Yu}, Ziyi Guo, Simone Campanoni, Peter Dinda, Xinyu Xing} \\
    \textit{USENIX Security Symposium 2024}
  }
  \resumeSubItem{
    \textbf{FIRST: Exploiting the Multi-Dimensional Attributes of Functions for Power-Aware Serverless Computing} \\
    \textit{Lu Zhang, Chao Li, Xinkai Wang, Weiqi Feng, \textbf{Zheng Yu}, Quan Chen, Jingwen Leng, Minyi Guo, Pu Yang, Shang Yue} \\
    \textit{IEEE International Parallel and Distributed Processing Symposium (IPDPS) 2023}
  }
\resumeSubHeadingListEnd

\section{Professional Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {DepthFirst, AI. Inc}{San Francisco, CA, US}
    {Security Research Engineer}{March 2026 -- Present}
    \resumeItemListStart
      \resumeItem{\textbf{Web \& Application Security:} Developing LLM-based agent systems for automated vulnerability discovery in web applications, targeting both frontend and backend components written in high-level languages. Agents autonomously identify and exploit classes such as XSS, SQLi, SSRF, IDOR, authentication bypass, and business-logic flaws.}
      \resumeItem{\textbf{Low-Level System Security:} Building automated vulnerability discovery systems for programs written in low-level languages (C/C++), including memory corruption bugs (buffer overflows, use-after-free, format strings) and logic vulnerabilities in system software.}
      \resumeItem{\textbf{Automated Penetration Testing:} Designing end-to-end agentic pipelines that conduct full penetration testing engagements autonomously—covering reconnaissance, attack surface enumeration, exploitation, and impact verification across heterogeneous environments.}
    \resumeItemListEnd
  \resumeSubheading
    {Certified Kernel Tech LLC}{New York, NY, US}
    {Security Researcher}{Jan 2026 -- March 2026}
    \resumeItemListStart
      \resumeItem{Developed LLM-based agents for automated smart contract vulnerability discovery and analysis}
      \resumeItem{Conducted smart contract vulnerability research across multiple platforms including Solidity, Move, and Solana}
    \resumeItemListEnd
  \resumeSubheading
    {University of Waterloo}{Waterloo, ON, Canada}
    {Visiting Graduate Researcher -- CrySP Lab (Advisor: Prof. Meng Xu)}{Jun 2025 -- Sep 2025}
    \resumeItemListStart
      \resumeItem{Conducted patch validation research to verify the correctness of vulnerability repairs across open-source projects.}
      \resumeItem{Designed and evaluated techniques for detecting incomplete or incorrect patches.}
    \resumeItemListEnd
  % \resumeSubheading
  %   {Google Summer of Code (Part-time)}{Remote}
  %   {Project Mentor -- Qiling Framework}{Apr 2022 -- Oct 2022}
  %   \resumeItemListStart
  %     \resumeItem{Mentored international contributors on MCU emulation and firmware analysis implementations.}
  %     \resumeItem{Guided development of RISC-V and Cortex-M architecture support for the Qiling emulation framework.}
  %   \resumeItemListEnd
  \resumeSubheading
    {JD.COM, Inc.}{Beijing, China}
    {Security Engineer -- Application Security Team}{Jun 2021 -- May 2022}
    \resumeItemListStart
      \resumeItem{Conducted vulnerability research and security assessments for large-scale e-commerce infrastructure.}
      \resumeItem{Developed automated security testing tools and contributed to internal security training programs.}
    \resumeItemListEnd
  % \resumeSubheading
  %   {Shanghai Jiao Tong University}{Shanghai, China}
  %   {Infrastructure Engineer -- Information and Network Center}{Sep 2019 -- May 2021}
  %   \resumeItemListStart
  %     \resumeItem{Maintained and optimized university-wide computing infrastructure serving 40,000+ users.}
  %     \resumeItem{Implemented monitoring solutions and performance improvements for critical campus systems.}
  %   \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Teaching Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Operating Systems (COMP\_SCI 343)}{Sep 2025 -- Dec 2025}
    {Graduate Teaching Assistant, Northwestern University}{Instructor: Dr. Branden Ghena}
  \resumeSubheading
    {Introduction to Computer Security (COMP\_SCI 350)}{Sep 2024 -- Dec 2024}
    {Graduate Teaching Assistant, Northwestern University}{Instructor: Prof. Xinyu Xing}
  \resumeSubheading
    {Programming Design and Data Structures (CS151)}{Jun 2019 -- Sep 2019}
    {Undergraduate Teaching Assistant, Shanghai Jiao Tong University}{Instructor: Prof. Huiyu Weng}
\resumeSubHeadingListEnd





\section{Selected Projects}
\resumeSubHeadingListStart
  \resumeProjectHeading
      {\textbf{PortGPT} $|$ \emph{LLM-based Automated Patch Backporting}}{\href{https://github.com/OS3Lab/patch-backporting}{[\underline{GitHub}]}}
      \resumeItemListStart
        \resumeItem{Engineered an LLM-powered system for automatically backporting security patches across software versions, addressing a critical challenge in software maintenance that traditionally requires significant manual expert effort.}
        \resumeItem{Implemented novel prompt engineering techniques and validation mechanisms to ensure backport correctness.}
      \resumeItemListEnd

  \resumeProjectHeading
      {\textbf{PatchAgent} $|$ \emph{AI-Powered Program Repair System}}{\href{https://github.com/cla7aye15I4nd/PatchAgent}{[\underline{GitHub}]}}
      \resumeItemListStart
        \resumeItem{Built an intelligent program repair agent that mimics human debugging workflows using large language models, achieving state-of-the-art performance on standard benchmarks and recognition as a DARPA AIxCC finalist.}
        \resumeItem{Designed multi-stage repair pipeline incorporating static analysis, dynamic testing, and iterative refinement.}
      \resumeItemListEnd

  \resumeProjectHeading
      {\textbf{ShadowBound} $|$ \emph{Compiler-Based Memory Safety}}{\href{https://github.com/cla7aye15I4nd/ShadowBound}{[\underline{GitHub}]}}
      \resumeItemListStart
        \resumeItem{Developed novel heap memory protection mechanism using advanced metadata management and LLVM-based compiler optimizations, achieving significant performance improvements over existing solutions.}
        \resumeItem{Implemented custom LLVM passes for fine-grained memory instrumentation with minimal runtime overhead.}
      \resumeItemListEnd

  \resumeProjectHeading
      {\textbf{GPT-Fuzzer} $|$ \emph{LLM Security Testing Framework}}{\href{https://github.com/sherdencooper/GPTFuzz}{[\underline{GitHub}]}}
      \resumeItemListStart
        \resumeItem{Created scalable fuzzing infrastructure for evaluating LLM safety properties and jailbreak resistance, now integrated into Microsoft Azure's PyRIT security toolkit used by enterprise customers worldwide.}
        \resumeItem{Pioneered template-based generation techniques for systematic exploration of prompt injection vulnerabilities.}
      \resumeItemListEnd

  \resumeProjectHeading
      {\textbf{Qiling Framework} $|$ \emph{Advanced Binary Emulation}}{\href{https://github.com/qilingframework/qiling}{[\underline{GitHub}]}}
      \resumeItemListStart
        \resumeItem{Core contributor to multi-platform binary emulation framework with 5,000+ GitHub stars. Implemented comprehensive MCU emulation module supporting STM32, GigaDevice, and SiFive microcontrollers across ARM Cortex-M and RISC-V architectures.}
        \resumeItem{Extended firmware analysis capabilities and integrated AFL fuzzing support for embedded systems testing.}
      \resumeItemListEnd

  \resumeProjectHeading
      {\textbf{Pymx Compiler} $|$ \emph{Educational Compiler Infrastructure}}{\href{https://github.com/cla7aye15I4nd/Pymx}{[\underline{GitHub}]}}
      \resumeItemListStart
        \resumeItem{Designed and implemented a complete compiler for Java-like language targeting RISC-V architecture, featuring lexical analysis, parsing, semantic analysis, optimization passes, and code generation to RV32IM assembly.}
      \resumeItemListEnd

  \resumeProjectHeading
      {\textbf{RISC-V CPU Implementation} $|$ \emph{Hardware Design}}{\href{https://github.com/cla7aye15I4nd/trivial-riscv-cpu}{[\underline{GitHub}]}}
      \resumeItemListStart
        \resumeItem{Architected RISC-V processor in Verilog HDL implementing Tomasulo algorithm for out-of-order execution, with instruction cache, load buffer, and branch prediction for enhanced performance on FPGA platforms.}
      \resumeItemListEnd
\resumeSubHeadingListEnd


\section{Honors \& Awards}
    \resumeSubHeadingListStart
        \resumeSubheading
        {CSAW Applied Research Competition Finalist / Runner-up in Technical Impact Award}{2025}
        {NYU Tandon School of Engineering -- PatchAgent Project}{}
        \resumeSubheading
        {USENIX Security Student Grant Recipient}{2024, 2025}
        {USENIX Association}{}
        \resumeSubheading
        {DARPA AIxCC Advanced Finals}{2024}
        {Top Finalist -- Team 42-b3yond-6ug}{}
        \resumeSubheading
        {ACM CCS Student Grant Recipient}{2024}
        {ACM SIGSAC Conference on Computer and Communications Security}{}
        \resumeSubheading
        {DEFCON CTF Finals -- 5th Place}{2023}
        {Team StrawHat (7th Place in 2022)}{}
        \resumeSubheading
        {Outstanding Graduate Award}{2022}
        {Shanghai Jiao Tong University}{}
        \resumeSubheading
        {Zhiyuan Honor Scholarship}{2018--2021}
        {Shanghai Jiao Tong University (Top 2\% annually)}{}
        \resumeSubheading
        {China National Olympiad in Informatics -- Silver Medal}{2017}
        {China Computer Federation (CCF) -- Top 100 Nationally}{}
    \resumeSubHeadingListEnd


\section{Conference Presentations}
\resumeSubHeadingListStart
  \resumeSubheading
    {Reversing MCU with Firmware Emulation}{Dec 2022}
    {BlackHat Europe}{London, UK}
\resumeSubHeadingListEnd


\section{Academic Service}
\resumeSubHeadingListStart
  \resumeSubheading
    {Program Committee Member}{}
    {AI/ML/SE Conferences}{}
    \resumeItemListStart
        \resumeItem{LLM4Code Workshop, co-located with ICSE -- 2026}
        \resumeItem{International Conference on Learning Representations (ICLR) -- 2025, 2026}
        \resumeItem{Conference on Neural Information Processing Systems (NeurIPS) -- 2024, 2025}
        \resumeItem{International Conference on Machine Learning (ICML) -- 2025}
        \resumeItem{Artificial Intelligence and Statistics (AISTATS) -- 2025}
        \resumeItem{AAAI Undergraduate Consortium (AAAI-UC) -- 2025}
        \resumeItem{ICECI -- 2024}
    \resumeItemListEnd
  \resumeSubheading
    {Artifact Evaluation Committee Member}{}
    {Security \& Systems Conferences}{}
    \resumeItemListStart
        \resumeItem{ACM Conference on Computer and Communications Security (CCS) -- 2023, 2024, 2025}
        \resumeItem{USENIX Security Symposium -- 2024, 2025}
        \resumeItem{Network and Distributed System Security Symposium (NDSS) -- 2025}
        \resumeItem{USENIX Annual Technical Conference (ATC) -- 2024}
        \resumeItem{Operating Systems Design and Implementation (OSDI) -- 2024}
        \resumeItem{International Symposium on Software Testing and Analysis (ISSTA) -- 2024}
    \resumeItemListEnd
  \resumeSubheading
    {Peer Reviewer}{}
    {Academic Journals}{}
    \resumeItemListStart
        \resumeItem{IEEE Transactions on Dependable and Secure Computing (TDSC)}
        \resumeItem{PeerJ Computer Science}
        \resumeItem{IEEE Transactions on Information Forensics and Security (TIFS)}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


\section{Technical Skills}
    \begin{itemize}[leftmargin=0.15in, label={}]
    \item{
        \textbf{Programming Languages}{: C/C++ (Expert), Python (Expert), Rust, Java, JavaScript/TypeScript, Go, OCaml, Verilog HDL} \\
        \textbf{Security \& Binary Analysis}{: IDA Pro, Ghidra, Angr, Unicorn Engine, Qiling Framework, Binary Ninja, GDB} \\
        \textbf{AI/ML Frameworks}{: PyTorch, LangChain, Transformers, OpenAI API, Anthropic API} \\
        \textbf{Systems \& Compilers}{: LLVM/Clang, GCC, Linux Kernel Development, QEMU, Unicorn} \\
        \textbf{Development Tools}{: Git, Docker, Kubernetes, CI/CD (GitHub Actions, Jenkins), Vivado, VSCode, Emacs} \\
        \textbf{Databases \& Infrastructure}{: MySQL, PostgreSQL, Redis, Apache Spark, Elasticsearch} \\
        \textbf{Languages}{: English (Fluent), Chinese (Native)}
    }
    \end{itemize}


%-------------------------------------------
\end{document}
